---
title: "Public Bike Sharing Data Visualization"
author: "R package build"
date: '2021-09-02'
slug: []
categories: Data World
tags:
- Data Visualization
- R
Description: ''
Tags: []
Categories: []
DisableComments: no
thumbnail: images/bike-sharing.jpg
---

Main focus of this artical is to explore the data visulization packages _ggplot2_ and _ggridges_

Today we will use the dataset from [__Kaggle: Mark Kaghazgarian__](https://www.kaggle.com/marklvl/bike-sharing-dataset)

Packages needed are listed below:

```{r message=FALSE}
library(ggplot2) 
library(dplyr)
library(ggridges) ## ridge line plot
library(hrbrthemes)
library(viridis)
library(lubridate) ##dealing with date/time
library(tidyverse)
library(gganimate)
```

Here is the data:

```{r}
bike_data <- read.csv('~/DATASETS/archive/day.csv')
str(bike_data)
```

This data set recorded the public bike rental count from 2011 to 2012 in Washington D.C., and all other weather related information.

Before proceeding with some plots, lets tidy up the data a bit.

```{r}
bike_data <- bike_data[-1] ## first column is just index number
bike_data$dteday <- as.Date(bike_data$dteday, format = '%Y-%m-%d')
bike_data[,c(2:8)] <- lapply(bike_data[,c(2:8)], factor) ##integer in these columns represent different factors/levels, detailed data background info https://www.kaggle.com/marklvl/bike-sharing-dataset
```

Say, if I wanted to know how the bike rental count was distributed along four different seasons in the year of 2011.

```{r}
levels(bike_data$season) <- c('Spring', 'Summer', 'Fall', 'Winter')
bike_2011 <- bike_data[1:365, ]
bike_2012 <- bike_data[366:730, ]##get the 2011/2012 data

bike_2011 %>% plot(x = bike_2011$season, y = bike_2011$cnt)
```

Pretty boring, isn't it? Lets see how we can make better plots with _ggplot2_ and _ggridges_

Lets see how total bike rental counts are distributed along 4 seasons:
```{r message=FALSE}
bike_2011 %>% ggplot(aes(x = cnt, y = season,fill = season)) +
  geom_density_ridges(lwd = 0)+
  scale_fill_manual(name = 'Season', values = c("#05f5dd", '#BCFA09','#FA9409','#F3ECF0'))+
  theme_ridges() +
  theme(legend.position = "bottom") +
  labs(title = "Public Bike Rental in Washington D.C.", subtitle = "2011")+
  xlab('Bike Count')
```

This is how temperatures of each month in 2011 feels like:
```{r message=FALSE}
bike_2011 %>% ggplot(aes(x= temp*50, y = mnth, fill = stat(x))) +
  geom_density_ridges_gradient(scale = 2, rel_min_height = 0.01, lwd = 0.2, quantile_lines = TRUE, color = 'white')+
  scale_fill_viridis(name = 'Temperature', option = 'C')+
  labs(title = 'Temperatures in Washington D.C.(2011)') +
  ylab('Month')+
  xlab("Temperature(Celcius)")+
  theme_ridges()
```

What if I want to compare the weekly average bike rental count between 2011 and 2012, in a cool way? You can use _gganimate_ package to do a animation plot.

```{r message=FALSE}
bike_1 <- bike_data[1:730, ]
bike_1$dteday <- week(bike_1$dteday) ##week() function from lubridate, to get week number

by_week <- bike_1 %>% group_by(dteday, yr) %>% summarise(
  mean_cnt = mean(cnt))

by_week %>% ggplot(aes(x = dteday, y = mean_cnt, group = yr, color = yr))+
  geom_line()+
  scale_color_viridis(discrete = TRUE)+
  theme_ipsum()+
  scale_color_manual(name = 'Year',labels = c('2011','2012'), values = c("#04FBE1", "#02A9FD"))+
  ggtitle("Bike Rental in 2011 and 2012")+
  xlab("Weekly Average")+
  transition_reveal(dteday)
```

Pretty awesome, right?
...
Who you taling to? No one is reading you blog, Lee
..
..
...
....
Its ok
